COVID-19 Municipalities

### 2020-05-12 COVID-19 Municipalities v0.Rmd

# gridExtra::grid.arrange(p1,p2,nrow=1)
```
** Cataluña 30 de Marzo**
```{r cat-p1}
p1
```
** Cataluña 30 de Abril**
```{r cat-p2}
p2
```

@@

** País Vasco 20 de Marzo - 20 Abril**
```{r pv-p1}
p1
```
** País Vasco 26 de Abril**
```{r pv-p2}
p2
```

@@

q <- quantile(madrid.sf$I04May)
madrid.sf$Quantile<- as.factor((madrid.sf$I04May > q[2]) + (madrid.sf$I04May > q[3]) +(madrid.sf$I04May >= q[4]) + 1)
p2 <- ggplot(data = madrid.sf) +
  geom_sf(aes(fill = Quantile),color = "black",size=.2) +
  theme_bw(base_size=6) +
  scale_fill_manual(values=c("#FFFEDE","#FFDFA2", "#FFA93F", "#D5610D"))
```
**Madrid de 8 de Abril**
```{r mad-p1}
p1
```
**Madrid de 4 de Mayo**
```{r mad-p2}
p2
```

>>>>

# gridExtra::grid.arrange(p1,p2,nrow=1)
```

**Cataluña 30 de Marzo**
```{r cat-p1}
p1
```

**Cataluña 30 de Abril**
```{r cat-p2}
p2
```

@@

**País Vasco 20 de Marzo**
```{r pv-p1}
p1
```

**País Vasco 20 de Abril**
```{r pv-p2}
p2
```

@@

q <- quantile(madrid.sf$I04May)
madrid.sf$Quantile<- as.factor((madrid.sf$I04May > q[2]) + (madrid.sf$I04May > q[3]) +(madrid.sf$I04May >= q[4]) + 1)
p2 <- ggplot(data = madrid.sf) +
  geom_sf(aes(fill = Quantile),color = "black",size=.2) +
  theme_bw(base_size=6) +
  scale_fill_manual(values=c("#FFFEDE","#FFDFA2", "#FFA93F", "#D5610D"))
```

**Madrid de 8 de Abril**
```{r mad-p1}
p1
```

**Madrid de 4 de Mayo**
```{r mad-p2}
p2
```
